Top-Down Graph-Based Neuron Reconstruction

### 2017-11-15 papers/cvpr2018/3_evaluation.tex
paper: updated figures and added HP edits

% !TEX root =  paper.tex
\section{Evaluation}
In this section, we describe the dataset, evaluation metric ...
\donglai{current organization is a bit unnatural.. too much details/overhead for the experiment setup, which can be put in the supplementary}

@@

\noindent\textbf{Kasthuri.}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. This dataset is $5342 \times 3618 \times 338$ voxels in size. The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. We evaluate our methods using the left cylinder of this 3-cylinder dataset. We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. We divide the dataset into two volumes along the $x$ dimension where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.

@@

\subsection{Pixel-Based Segmentation Pipelines}
\label{sec:neuroproof}

The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data. We learn 3D affinities using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}. We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.

@@

\subsection{Error Metric}
\label{sec:variation-of-information}

We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing} (VI-s). Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$.
Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively. Since we are measuring the entropy between two clusterings, better VI scores are closer to the origin.
In Fig.~\ref{fig:variation-of-information}, we compute VI scores for the input over-segmentation at different stopping thresholds of agglomeration.

\subsection{Graph Creation Parameters}

There are two essential parameters to the edge generation algorithm described in Section~\ref{sec:skeletonization}: $t_{low}$ and $t_{high}$. Ideally, the merge candidates output by this algorithm will contains all possible positive examples with a very limited number of negative examples. After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produce the best results considering this objective.

>>>>

% !TEX root =  paper.tex
\section{Experimental Results}

We evaluate our method on two connectomics datasets and compare it to a state-of-the-art pixel-based reconstruction method using the variation of information (VI) metric.
\hp{depending on space we can shorten this and put details into the supplemental material}

@@

\noindent\textbf{Kasthuri.}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. This dataset is $5342 \times 3618 \times 338$ voxels in size. The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. We evaluate our methods using the left cylinder of this 3-cylinder dataset. We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.

@@

\subsection{Pixel-Based Segmentations}
\label{sec:neuroproof}

The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data. We learn 3D affinities using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}. We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}. We use this segmentation as our baseline for comparisons with our method.

@@

\subsection{Graph Generation Parameters}

There are two essential parameters to the graph generation algorithm described in Section~\ref{sec:skeletonization}: $t_{low}$ and $t_{high}$. Ideally, the merge candidates output by this algorithm will contains all possible positive examples with a very limited number of negative examples. After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produce the best results considering this objective.

### 2017-11-15 papers/cvpr2018/4_results.tex
paper: updated figures and added HP edits

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-microns-train-600.png}
	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-microns-test-600.png}
	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
	\caption{Our improvement (reD) on variation of information from the baseline NeuroProof segmentation (green). The blue dot represents an oracle which correctly partitions the graph.}
	\label{fig:variation-of-information}
\end{figure*}

@@

We compute the variation of information for our segmentations against the expert-labeled ground truth datasets. 
The input segmentation to our network serves as a baseline. 
We evaluate NeuroProof (our input) at several different thresholds to create a variation of information curve. 
Figure \ref{fig:variation-of-information} shows the results on the datasets compared to the baseline (green) and an oracle (blue). 
The oracles sees the graph from our algorithm and correctly partitions the graph based on the ground truth. 
%TODO{Our methods decreases the split variation of information by a factor of XX\% and only increases the merge variation of information by a factor of XX\% on the test datasets.}
Figure \ref{fig:positive-results} shows some successful merges on the Kasthuri Vol. 2. 
Several of these successful examples combine multiple consecutive segments. 
The third example shows the correction of an oversegmented dendrite. 
Figure \ref{fig:negative-results} shows some errors made. 
In two of these examples the algorithm correctly predicted several merges but made just one error.
In the third example, an error in the initial segmentation propagated in our pipeline. 
In the next three subsections we show how each step in the pipeline contributes to this final result.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct1.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct2.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct3.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct4.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct5.png}
	\caption{Some correctly predicted results from our framework.}
	\label{fig:positive-results}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect1.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect2.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect3.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect4.png}
	\caption{Mistakes made by the proposed framework.}
	\label{fig:negative-results}
\end{figure}

\subsection{Pruning via Skeletonization}

\begin{table}
	\centering
	\small
	\begin{tabular}{c c c} \hline
		\textbf{Dataset} & \textbf{Baseline} & \textbf{After Pruning} \\ \hline
		Kasthuri Vol. 1 & 763 / 21242 (3.47\%) & 753 / 3459 (17.88\%) \\
		Kasthuri Vol. 2 & 1010 / 26073 (3.73\%) & 904 / 4327 (17.28\%) \\
		FlyEM Vol. 1 & 269 / 14875 (1.78\%) & 262 / 946 (21.69\%) \\
		FlyEM Vol. 2 & 270 / 16808 (1.58\%) & 285 / 768 (27.07\%)\\ \hline
	\end{tabular}
	\caption{The results of our pruning heuristic compared to the current baseline.}
	\label{table:skeletonization}
\end{table}

Table \ref{table:skeletonization} shows the results of pruning using the skeletonization heuristic.
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations.
This edge pruning is essential for the graph partitioning algorithm which has a computational complexity dependence on the number of edges. 
Our pruning heuristic removes at least $6\times$ the number of edges between correctly split segments on all datasets, achieving a maximum removal ratio of $20\times$. 
Equally important is the number of split errors that remain after pruning.
These are the locations that we want to merge to create a more accurate reconstruction.
For every dataset, the number of positive candidates remains relatively even. 
However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning. 
In fact, our method finds a number of examples which are non-adjacent.
Figure \ref{fig:skeleton-results} shows two example segments which are split errors.
The top example our algorithm missed but the segments are adjacent. 
The bottom example our algorithm found despite the fact that they are not adjacent.

@@

Table \ref{table:classification} shows the precision and recall for all of the datasets. 
Since, our method does not rely on the image data, we can train the network on an anisotropic dataset and get impressive results on an isotropic dataset.

\begin{table}[h]
	\centering
	\begin{tabular}{c c c c} \hline
		\textbf{Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{Accuracy} \\ \hline
		Kasthuri Training & 0.919 & 0.936 & 0.974 \\
		Kasthuri Testing & 0.737 & 0.717 & 0.907 \\
		FlyEM Vol. 1 & 0.796 & 0.478 & 0.862 \\ 
		FlyEM Vol. 2 & 0.762 & 0.422 & 0.810 \\ \hline
	\end{tabular}
	\caption{Precision and recall for the training and three test datasets.}
	\label{table:classification}
\end{table}

@@

Applying a graph-based optimization strategy increases the accuracy over the CNN alone. 
In our test datasets, we note an increase in precision on all datasets. 
For our segmentation problems we prefer a higher precision since it is more difficult to correct merge-errors. 
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all three datasets in relation to the CNN.

>>>>

% !TEX root =  paper.tex

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-train-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-test-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth.}
	\label{fig:variation-of-information}
\end{figure*}

@@

\subsection{Error Metric}
\label{sec:variation-of-information}

We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing} (VI-s). Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$.
Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively. Since we are measuring the entropy between two clusterings, better VI scores are closer to the origin.

In Fig.~\ref{fig:variation-of-information}, we show VI scores for the input over-segmentation of the Kasthuri data \hp{check} at different thresholds of agglomeration (green) compared to our method (red). We also show the comparison to an oracle (blue) that correctly partitions the graph from our algorithm based on ground truth. \hp{add discussion of the results}

%The oracles sees the graph from our algorithm and correctly partitions the graph based on the ground truth.
%TODO{Our methods decreases the split variation of information by a factor of XX\% and only increases the merge variation of information by a factor of XX\% on the test datasets.}

Fig.~\ref{fig:positive-results} shows successful merges on the Kasthuri Vol. 2. Several of these successful examples combine multiple consecutive segments. The third example in the figure shows the correction of an over-segmented dendrite.
Fig.~\ref{fig:negative-results} shows some failure cases. In two of these examples the algorithm correctly predicted several merges and made one error.
In the third example a catastrophic merge error \hp{check} in the initial segmentation propagated to the output. We now analyze how each major component of our method contributes to the final result.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct1.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct2.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct3.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct4.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct5.png}
	\caption{Correctly segmented neurons from our method.}
	\label{fig:positive-results}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect1.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect2.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect3.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect4.png}
	\caption{Errors made by our method.}
	\label{fig:negative-results}
\end{figure}

\subsection{Graph Creation}

\begin{table}
	\centering
	\small
	\begin{tabular}{c c c} \hline
		\textbf{Dataset} & \textbf{Baseline} & \textbf{After Pruning} \\ \hline
		Kasthuri Vol. 1 & 763 / 21242 (3.47\%) & 753 / 3459 (17.88\%) \\
		Kasthuri Vol. 2 & 1010 / 26073 (3.73\%) & 904 / 4327 (17.28\%) \\
		FlyEM Vol. 1 & 269 / 14875 (1.78\%) & 262 / 946 (21.69\%) \\
		FlyEM Vol. 2 & 270 / 16808 (1.58\%) & 285 / 768 (27.07\%)\\ \hline
	\end{tabular}
	\caption{The results of our skeleton graph pruning heuristic compared to the baseline segmentation.}
	\label{table:skeletonization}
\end{table}

Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the heuristic discussed in Sec.~\ref{sec:skeletonization}. The baseline algorithm considers all adjacent regions for merging. Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations. This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges. Our pruning heuristic removes at least $6\times$ the number of edges between correctly split segments on all datasets, achieving a maximum removal ratio of $20\times$.

Equally important is the number of split errors that remain after pruning. These are the locations that we want to merge to create a more accurate reconstruction. For every dataset, the number of positive candidates \hp{what is a positive candidate?} remains relatively equal. \hp{equal to what?}
However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning. In fact, our method finds a number of examples that are non-adjacent. Figure \ref{fig:skeleton-results} shows two example segments with split errors, one that our algorithm missed (top) and one that it identified (bottom), despite the fact that the split segments are not adjacent.

@@

Table \ref{table:classification} shows the precision and recall rates for all of the datasets. We can train the CNN on anisotropic data and get good results on isotropic data. \hp{add more discussion}

\begin{table}[h]
	\centering
	\begin{tabular}{c c c c} \hline
		\textbf{Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{Accuracy} \\ \hline
		Kasthuri Training & 0.919 & 0.936 & 0.974 \\
		Kasthuri Testing & 0.737 & 0.717 & 0.907 \\
		FlyEM Vol. 1 & 0.796 & 0.478 & 0.862 \\
		FlyEM Vol. 2 & 0.762 & 0.422 & 0.810 \\ \hline
	\end{tabular}
	\caption{Precision and recall rates for the training and three test datasets.}
	\label{table:classification}
\end{table}

@@

Applying a graph-based optimization strategy increases the accuracy over the CNN alone. In our test scores, we note an increase in precision on all datasets. For our segmentation problems we prefer a higher precision since it is more difficult to correct merge-errors. Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all three datasets in relation to the CNN without graph-based optimization. \hp{add more discussion}

### 2017-11-15 papers/cvpr2018/5_conclusions.tex
paper: major changes
paper: updated figures and added HP edits

\section{Conclusions}

\begin{itemize}
	\item Impact
	\item Future work
\end{itemize}

>>>>

% !TEX root =  paper.tex
\section{Conclusions}

We present a novel method for reconstructing neuronal processes in connectomics datasets. We extend existing pixel-based reconstruction strategies using a morphological 3D skeleton graph and show significant accuracy improvement on two datasets from two different species. Our approach enables enforcing domain-constraints on the resulting segmentation. We believe this approach extends beyond connectomics to other domains with different constraints.
\hp{add more future work}
